---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sphericaldistributions

<!-- badges: start -->
[![R-CMD-check](https://github.com/LMJL-Alea/sphericaldistributions/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/LMJL-Alea/sphericaldistributions/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/LMJL-Alea/sphericaldistributions/graph/badge.svg)](https://app.codecov.io/gh/LMJL-Alea/sphericaldistributions)
<!-- badges: end -->


The goal of sphericaldistributions is to have many different statistical distributions on the sphere in one package. It allows to test easily multiple distribution when working with a fitting data set. We provide methods to compute the MLE, PDF, CDF, random number generation, and parameter estimation for each of the distribution, making it easy to compare and use each of them.

## Installation

You can install the development version of sphericaldistributions from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("LMJL-Alea/sphericaldistributions")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(sphericaldistributions)
## basic example code
x <- rwatson(100, c(1, 0, 0), 10)

```

## Acknoledgment
This package is based on the Anima library, RRID:SCR_017017.
